---
title: "MA [46]15 Homework 5"
author: "**`[==[`**Your Name**`]==]`**"
format: gfm
---


## Question 1


In this work I'll analyze the titles of the most recent 10,000 papers in the
[Criminal Justice category](https://www.ssrn.com/index.cfm/en/cjrn/) of the
[Social Science Research Network](https://www.ssrn.com/index.cfm/en/) preprint
repository. The data in file `data/ssrn_cjn.rds` is loaded into the table
`papers`. As an initial check, I'm plotting the distribution of number of words
in title for each year.


**`[==[`**
Modify the `q1` chunk below to load `ssrn_cjn.rds` into the dataset `papers`.
Create a new variable `word_count` with the number of words in each title and
then make boxplots of number of words per title for each year. Write a short
assessment about the variability of title sizes over the years. How many papers
have exactly one word in the title?
**`]==]`**

```{r q1}
suppressPackageStartupMessages(library(tidyverse))
```



## Question 2

**`[==[`**
Modify chunk `q2` below to "cross" each title in `papers` with each keyword in
`keywords` and then check if each title contains each keyword. Before checking,
however, convert the words in the title to lower case since the keywords are all
in lower case. Store the outcome of the check, `FALSE` if keyword is absent,
`TRUE` if present in title, in a new variable called `keyword_in_title`. Then,
for each year and keyword, count the total number of times papers with each
keyword were downloaded; stored in variable `n`. Finally, using `pivot_wider`,
cross-tabulate these counts for the last ten years by indexing rows by year and
columns by keyword. Your final table should like the output of this chunk but
with different numbers.

```{r q2-info}
#| echo: false
# Delete this chunk before you submit
# This is just to illustrate what your resulting table should look like
tibble::tribble(
  ~year, ~crimin, ~eviden, ~international, ~justice, ~polic, ~right, ~violen,
   2018,   1461L,    747L,           198L,    1240L,  1656L,   171L,    371L,
   2019,   1573L,   1061L,          1708L,     936L,   820L,   929L,   2032L,
   2020,   1812L,   2071L,           200L,     295L,   165L,  1626L,   1724L,
   2021,    718L,   1506L,           687L,     609L,   439L,   776L,   1323L,
   2022,   2054L,   2057L,           652L,     812L,  1071L,  1952L,   1804L,
   2023,   1034L,   1861L,          1349L,     145L,   255L,  1413L,   1706L
  )
```
**`]==]`**

```{r q2}
keywords <- tibble(keyword = 
                     c("crimin", "justice", "polic", 
                       "eviden", "violen", "right", "international")
                   )
# example of crossing between two tables:
crossing(tibble(x = 1:3), tibble(y = letters[1:3]))
```


## Question 3

**`[==[`**
It's hard to assess counts in a table, so, in a chunk labeled `q3`, make a
line plot of the counts you computed in Question 2, one line per keyword
(color each line by keyword). Comment on any specific patterns; for instance,
what seems to be the most commonly downloaded keyword? Any keywords declining or
increasing in interest?
**`]==]`**



## Question 4

**`[==[`**
The counts for some keyword can be changing simply because the number of overall
downloads is changing with the years. Thus, instead of plotting counts, make
line plots of the **proportion** of total downloads in each year that had each
keyword in their titles. To this end, in a `q4` chunk, first create a new
dataset called `papers_year` with the counts of the total downloads per year and
then **join** this with the title-keyword crossed dataset in Question 2. Then
compute a new variable called `prop` with the proportion of titles containing
each keyword by year. Finally, create the plot. Do your conclusions change when
compared to the plot in Question 3? Comment.
**`]==]`**
